\chapter{Abstract}
This compendium of solved problems is intended to include the problems of David Tong Notes, Quantum Field Theory in a Nutshell by Zee, and A First Book of Quantum Field Theory. \\
The reasons for constructing this stationary are manifold. \\
On a personal level, we're engaged in an independent study of the subject, and having this resource at hand accelerates our ability to revisit various topics swiftly, maintaining a steady pace of progress. \\

Beyond personal use, the creation of this compendium also serves a broader purpose: to give back to the scientific community. This field of study has become more accessible to researchers over the past years, thanks to the collective contributions of countless scientists. We hope to extend this collaborative spirit by providing our own problem solutions. While we don't claim these solutions are perfect, we do aspire to present them with a level of detail that can assist anyone who may be struggling to understand the topic or offer a fresh perspective to those who are on a smoother path. We have no pretense of expertise on the subject, and the true value of this compendium is something we leave to the community to assess. Based on our experience, we believe that having detailed solutions can be a significant tool for deliberate learning. We welcome all contributions that help to correct any errors or fill in any gaps in the document. We view this compendium as an ongoing collaborative effort, where each correction or suggestion further refines this learning resource.\\

% \todo[inline]{Add new section about results in \cref{sec:fourth}.}